Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-10 chi/piecework/presentation/complexity.tex
final talk!?

\begin{frame}{George Airy}
    Airy built complexity into the process, assigning \emph{human computers} 
    to calculate \& verify the \emph{right ascension} and \emph{declination} of stars.

@@

\begin{frame}{Implications for On--Demand Work}
  Has technology shifted on--demand work?
    \begin{itemize}
      \item Technology makes \emph{some} complex tasks relatively trivial
      \item Measuring workers is easier than ever
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{George Airy}
    Airy built complexity into the process, assigning \emph{human computers} 
    to calculate astronomical movements.
    % to calculate \& verify the \emph{right ascension} and \emph{declination} of stars.

@@

\begin{frame}{Implications for On--Demand Work}
  Has technology shifted on--demand work?

  In some ways, yes
        \begin{itemize}
          \item Technology makes \emph{some} complex tasks relatively trivial
          \item Measuring workers is easier than ever
        \end{itemize}
  In other ways, no --- we still don't have good end--to--end processes for arbitrarily complex work

  \emph{We can make a routine out of building planes, but not out of fixing trains}
\end{frame}

### 2017-05-10 chi/piecework/presentation/introduction.tex
final talk!?

\begin{frame}{Introduction}
  We hope you come away with:
      \begin{itemize}
        \item An \alert{ontological lens} for making sense of on--demand work as a resurgence of piecework
        \item A renewed interest in the use of \alert{historical analysis} to make sense of contemporary phenomena
      \end{itemize}
\end{frame}

\begin{frame}{Comparative Historical Analysis}
  HCI researchers have used historical analysis in the past\par
  \scriptsize{\textcite{Wyche2006,bodker1993historical}\par}\normalsize{}

>>>>

% \begin{frame}{Introduction}
  % To take away:
      % \begin{itemize}
        % \item An \alert{ontological lens} for making sense of on--demand work as a resurgence of piecework
        % \item A renewed interest in the use of \alert{historical analysis} to make sense of contemporary phenomena
      % \end{itemize}
% \end{frame}

\begin{frame}{Comparative Historical Analysis}
  HCI researchers have used \alert{historical analysis} to understand social systems before\par
  \scriptsize{\textcite{Wyche2006,bodker1993historical}\par}\normalsize{}
